A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2017-04-04 EvoPar2017/paper.Rnw
Add running stuff
Producing PNGs too for poster

<<setup, cache=FALSE,echo=FALSE>>=
library("ggplot2")
library("RColorBrewer")

experiment.data <- data.frame(Experiment=character(),
                              milliseconds=character(),                           
                              IPs=character(), 
                              actualIPs=character(),
                              PUTs=character(),
                              actualPUTs=character(),
                              PUTratio = character(),
                              PUTsIP =character())

@@

\title{A performance assessment of evolutionary algorithms in
  volunteer computing environments: the importance of entropy}

\author{Juan-J.~Merelo\inst{1} \and Paloma de las Cuevas\inst{1} \and Pablo
  Garc\'ia-S\'anchez \inst{2} \and Mario Garc\'ia-Valdez \inst{3}}

\institute{Dept. of Computer Architecture and Technology, University
of Granada, Spain and CITIC, \email{(jmerelo,palomacd)@ugr.es} 
\and
Department of Computer Engineering, University of C\'adiz (Spain), \email{pablo.garciasanchez@uca.es}
\and
Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana, \email{amherag,mario@tectijuana.edu.mx}}

>>>>

<<setup, cache=FALSE,echo=FALSE>>=
library("ggplot2")
library("RColorBrewer")
opts_chunk$set( dev        = c("pdf", "png") )
experiment.data <- data.frame(Experiment=character(),
                              milliseconds=character(),                           
                              IPs=character(), 
                              actualIPs=character(),
                              PUTs=character(),
                              actualPUTs=character(),
                              PUTratio = character(),
                              PUTsIP =character())

@@

\title{A performance assessment of evolutionary algorithms in
  volunteer computing environments: the importance of entropy} 
%\titlerunning{A performance assessment of evolutionary algorithms in volunteer computing environments}

\author{Juan-J.~Merelo\inst{1} \and Paloma de las Cuevas\inst{1} \and Pablo
  Garc\'ia-S\'anchez \inst{2} \and Mario Garc\'ia-Valdez \inst{3}}
%\authorrunning{Merelo, de las Cuevas, García-Sánchez and García-Valdez}
\institute{Dept. of Computer Architecture and Technology, University
of Granada, Spain and CITIC, \email{(jmerelo,palomacd)@ugr.es} 
\and
Department of Computer Engineering, University of C\'adiz (Spain), \email{pablo.garciasanchez@uca.es}
\and
Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana, \email{amherag,mario@tectijuana.edu.mx}}
